---
title: "How to?"
author: "Jiddu Alexander"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

# Authenticate

First get an authentication token using labguru_authenticate.

```{r}
labguru_authenticate(email    = "my@@email.com",
                     password = "mypassword",
                     server   = "https://jonathan.labguru.com",
                     set_sys  = TRUE)
```

With set_sys = TRUE your system variables LABGURU_SERVER and LABGURU_TOKEN are automatically set and can be picked up by future function calls conencting to the Labguru API. Check these variables using labguru_sys_variables()

```{r}
labguru_sys_variables()
```

# Upload data to Labguru

You can now upload a dataset to Labguru using labguru_upload_dataset:

```{r}
labguru_upload_dataset(dataset    = mtcars,
                       name       = "mtcars",
                       desription = "Motor Trend Car Road Tests data")
```
