---
title: "ic50 integration"
author: "Jiddu Alexander"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```


# Introduction to the ic50 package

```{r}
library(ic50)
```

Functions within the ic50 package. 

- ic50() to launch the GUI
- hts.96() to analyse a plate with 96 wells
- hts.384() to analyse a a plate with 384 wells

```{r, eval=FALSE}
ic50()
```

Example of running the 384 wells analysis with local files.

```{r}
dir <- "../data-raw/ic50/experiment-001/"

r <- hts.384(indir     = paste0(dir, "Files"),
             plates    = 2,
             measure   = paste0(dir, "Suppl-files/mpi384_measure.txt"),
             control   = paste0(dir, "Suppl-files/mpi384_control.txt"),
             dilution  = paste0(dir, "Suppl-files/mpi384_dilution.txt"),
             inhib     = rep(0.5,7),
             outdir    = paste0(dir, "Output"),
             normalize = "mean",
             graphics  = "single")
class(r)
r
```


# Downloading plates data from a Labguru server

## Setting up Labguru connection

```{r}
# Load LabgururR locally

devtools::load_all()

# Authenticate

email    <- ""
password <- ""

labguru_authenticate(email, password)

```

## Download JSON data

Loading JSON for plate 271

```{r}
server <- Sys.getenv("LABGURU_SERVER")
token  <- Sys.getenv("LABGURU_TOKEN")
# "https://jonathan.labguru.com/api/v1/plates/271"
base_url <- server
path     <- "/api/v1/plates/271"
query    <- paste0("token=", token)

url <- httr::modify_url(url   = base_url, 
                        path  = path,
                        query = query)

resp <- httr::GET(url)

# Expect resp to be JSON 
if (httr::http_type(resp) != "application/json") {
  stop("API did not return JSON", call. = FALSE)
}

# Parse without simplifaction for consistency
parsed <- jsonlite::fromJSON(httr::content(resp, as = "text"), 
                             simplifyVector    = FALSE, 
                             simplifyDataFrame = TRUE, 
                             flatten           = TRUE)

# check for request error
if (httr::http_error(resp)) {
  stop(sprintf("API request failed [%s]\n%s", parsed$status, parsed$error), call. = FALSE)
}
```

## Explore data 

Further parse the JSON deom the data element

```{r}
prs_data <- jsonlite::fromJSON(parsed$data)
```

The parsed data has several elements:

```{r}
names(prs_data)
```

- 'wells' contains the measure, dilution and control data
- 'samples' contains information on the cell lines and compounds
- 'added_samples' contains the compound id's
- 'arrange_in' is unknown information
- 'properties' is unknown information

An overview of first 10 columns of data stored in 'samples'. In the first two columns are the id's and names of the compounds.

```{r}
prs_data$samples[1:10]
```


Information about the individual wells is stored in several data frames under prs_data\$wells\$samples_metadata. Each data frame contains the wells information for 1 compound and is named after the id of that compound. 

```{r}
names(prs_data$wells$samples_metadata)
```

A sample of compound 41, which we know from the samples data represents '17AAG'.

```{r}
head(prs_data$wells$samples_metadata["41"])
```

## Prepare data for ic50

Reorganise samples_metadata.

Assumptions:

- prs_data\$wells\$coordinates is in the same order as the samples_metadata data frames, hence we can column bind them.
- if samples_metadata concentration data is NA the other columns also do not hold valuable information, hence we can filter by it.
- if we filter concentration for NA all stocks data left is numeric
- if the serial_factor column is there then it is always a data frame with a value and symbol column with equal length.


```{r}
# PREPARE each compound data frame separately
dfs <- lapply(X   = prs_data$wells$samples_metadata, 
              FUN = function(d) { 
                # Add coordinates before filter
                d$coordinates <- prs_data$wells$coordinates
                # Serial_factor is a nested dataframe, unnest it
                if ("serial_factor" %in% names(d)) {
                  d$comp_serial_factor_value  <- d$serial_factor$value
                  d$comp_serial_factor_symbol <- d$serial_factor$symbol
                  d$serial_factor <- NULL
                }
                # Filter empty rows
                d <- d[!is.na(d$concentration), ]
                # as.numeric stocks now that only numreic data remains
                d$stocks <- as.numeric(d$stocks)
                
                d
              })
```

```{r}
# SUBSET the compound columns
# ASSUMPTION: The column prs_data$samples$collection_name will be "Compounds" if it is a compound. Can't be missing or spelt differently 
collection_names        <- prs_data$samples$collection_name
names(collection_names) <- prs_data$samples$id
nc <- collection_names[names(dfs)] == "Compounds"
```

```{r}
# BIND ROWS
comp <- Reduce(f = rbind, 
               x = dfs[nc])
names(comp)[1:2] <- paste("comp", names(comp)[1:2], sep = "_")
```

```{r}
# ASSUMPTION: THERE CAN ONLY BE ONE CELL LINE
df <- merge(dfs[!nc][[1]], comp, by.x = "coordinates", by.y = "coordinates")
```

```{r}
# TEST: CELL LINE AND COMPOUND SAME LENGTH
nrow(df) == nrow(dfs[!nc][[1]])
nrow(df) == nrow(comp)

# TEST: NO DUPLICATES IN COORDINATES
length(unique(df$coordinates)) == nrow(df)
```

```{r}
# ADD: compound names
compound_names        <- prs_data$samples$name
names(compound_names) <- as.character(prs_data$samples$id)
df$comp_name          <- unname(compound_names[as.character(df$comp_stocks)])
```

```{r}
# ADD row and col for printing
df$row <- vapply(substr(df$coordinates, 1, 1), function(c) { which(c == LETTERS) }, FUN.VALUE = numeric(1))
df$col <- as.numeric(gsub("[^0-9.-]+", "", df$coordinates))
```

```{r}
# ARRANGE: by row and col
df <- df[order( df[,"row"], df[,"col"] ),]

head(df, 20)
```

## Write measure file

```{r}
# ASSUMPTION: 1 compound per row
# CHECK: does it require equal columns per row
measure <- lapply(X   = unique(df$row),
                  FUN = function(r) {
                    d      <- df[df$row == r, ]
                    name   <- paste0('"', unique(d$comp_name)[1], '"')
                    coords <- paste0('"', d$row, ',', d$col, '"')
                    c(name, coords)
                  })
names(measure) <- paste0("row", seq_along(measure))
measure        <- as.data.frame(t(as.data.frame(measure)))

measure
```

```{r}
write.table(x         = measure, 
            file      = "measure_from_api.txt",
            append    = FALSE, 
            sep       = "\t", 
            row.names = FALSE, 
            col.names = FALSE, 
            quote     = FALSE)
```

## Write dilution file

```{r}
# ASSUMPTION: 1 compound per row
# CHECK: does it require equal columns per row
dilution <- lapply(X   = unique(df$row),
                   FUN = function(r) {
                     d      <- df[df$row == r, ]
                     name   <- paste0('"', unique(d$comp_name)[1], '"')
                     coords <- paste0('"', d$comp_concentration, '"')
                     c(name, coords)
                   })
names(dilution) <- paste0("row", seq_along(dilution))
dilution        <- as.data.frame(t(as.data.frame(dilution)))

dilution
```

```{r}
write.table(x         = dilution, 
            file      = "dilution_from_api.txt",
            append    = FALSE, 
            sep       = "\t", 
            row.names = FALSE, 
            col.names = FALSE, 
            quote     = FALSE)
```

# Write control file

```{r}
head(cntrl, 6)
```


```{r}
cntrl <- prs_data$wells[c("control", "coordinates")]
cntrl <- cntrl[cntrl$control, ]

# ADD row and col for printing
cntrl$row <- vapply(substr(cntrl$coordinates, 1, 1), function(c) { which(c == LETTERS) }, FUN.VALUE = numeric(1))
cntrl$col <- as.numeric(gsub("[^0-9.-]+", "", cntrl$coordinates))

# ADD compound name
# ASSUMTION: each row has only 1 compound name
temp                  <- unique(df[c("comp_name", "row")])
compound_names        <- temp$comp_name
names(compound_names) <- as.character(temp$row)
cntrl$comp_name       <- unname(compound_names[as.character(cntrl$row)])

# ASSUMPTION: 1 compound per row
# CHECK: does it require equal columns per row
control <- lapply(X   = unique(cntrl$row),
                  FUN = function(r) {
                    d      <- cntrl[cntrl$row == r, ]
                    name   <- paste0('"', unique(d$comp_name)[1], '"')
                    coords <- paste0('"', d$row, ',', d$col, '"')
                    c(name, coords)
                  })
names(control) <- paste0("row", seq_along(control))
control        <- as.data.frame(t(as.data.frame(control)))

control
```

```{r}
write.table(x         = control, 
            file      = "control_from_api.txt",
            append    = FALSE, 
            sep       = "\t", 
            row.names = FALSE, 
            col.names = FALSE, 
            quote     = FALSE)
```

# ic50 analysis

```{r}

```


## Store data

```{r}

```


## Store images

```{r}
pdf_img <- magick::image_read_pdf("dose_response_curves.pdf")
magick::image_info(pdf_img)
magick::image_write(pdf_img[1], "test.png")
```











# OLD STUFF

```{r}
# comp_id <- names(prs_data$wells$samples_metadata)
```

```{r}
# df <- mapply(prs_data$wells$samples_metadata, 
#              comp_id,
#              FUN = function(d, c) { 
#                names(d) <- paste(names(d), c, sep = "_") 
#                d
#              })
# df <- Reduce(cbind, df)
# View(df)
```






```{r}
head(prs_data$wells$samples_metadata[["41"]], 30)
```

```{r}
head(prs_data$wells$samples_metadata[["41"]], 30)
```







```{r}
names(prs_data)
```

```{r}
names(prs_data$wells)
names(prs_data$samples)
```

```{r}
prs_data[3:6]
```


```{r}
prs_data$samples
```

```{r}
head(prs_data$wells)
```


```{r}
str(prs_data)
```




```{r}
substr(parsed$data, 1, 3000)
```


```{r}
substr(parsed$data, 1, 1000)
```





